Scaling up the hyperparameter grid for Naomi

### 2023-07-04 src/dev_scale-grid/scale-grid.Rmd
Simplify and improve scale grid notebook! Add PC loadings plot! Start moving unit tests out into check report

The names of the hyperparameters are:

```{r}
(hypers <- names(fit$par))
```

There are `r length(hypers)` of them, if you'd like to count.
Including `r data.frame(hypers) %>% filter(str_detect(hypers, "^logit_")) %>% nrow()` on the logit scale, and `r data.frame(hypers) %>% filter(str_detect(hypers, "^log_")) %>% nrow()` on the log scale.

@@

(marginal_sd_plot <- data.frame(par = names(sd), sd = unname(sd)) %>%
  mutate(
    start = str_extract(par, "^[^_]+"),
    scale = fct_recode(start, "Log" = "log", "Logit" = "logit", "Other" = "OmegaT")
  ) %>%
  ggplot(aes(x = reorder(par, sd), y = sd, col = scale)) +
    geom_point(size = 2) +
    coord_flip() +
    scale_color_manual(values = c("#56B4E9","#009E73", "#E69F00")) +
    lims(y = c(0, 2)) +
    theme_minimal() +
    labs(x = "", y = "Marginal standard deviation", col = "Scale"))

ggsave("marginal-sd.png", plot = marginal_sd_plot, height = 3.5, w = 6.25)
```

@@

The total number of points for this grid is 2:

```{r}
prod(base_grid$level)
```

Let's try fitting this, and see how long it takes.
First prepare the data:

@@

```{r}
quad$modesandhessians[, 1:24] %>%
  pivot_longer(cols = everything()) %>%
  mutate(id = rep(1:24, times = 2)) %>%
  ggplot(aes(x = reorder(name, id), y = value)) +
    geom_point(alpha = 0.8) +
    labs(x = "", y = "Value") + 
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 1))
```

Interesting to note that for the Cholesky adapted grid with `levels = c(1, 1, ..., 2, 1, ..., 1)` we see variation in all of the dimensions greater than or equal to the 16th.
This is related to the Cholesky adaption being based on a lower triangular matrix.
To verify this, we can look at the differences between the two grid points:

```{r}
diff(as.matrix(quad$modesandhessians[, 1:24]))
```

@@

```{r}
#' This is what the base grid looks like
mvQuad::getNodes(base_grid)

base_grid_copy <- rlang::duplicate(base_grid)

@@

```{r}
mvQuad::rescale(base_grid_copy, m = quad$optresults$mode, C = Matrix::forceSymmetric(solve(quad$optresults$hessian)), dec.type = 1)
diff(mvQuad::getNodes(base_grid_copy))
```

@@

## Points of confusion

How does this approach interact with the rescaling which occurs in adaptive quadrature?
That is to say $z \mapsto \hat \theta + Lz$ with $LL^\top = H$.
Do each of the dimensions of $z$ reflect dimensions of $Lz$?

@@

(tv_plot <- ggplot(tv_df, aes(x = n, y = tv)) +
  geom_point() +
  geom_hline(yintercept = 0.9, col = "grey", linetype = "dashed") +
  annotate("text", x = 20, y = 0.875, label = "90% of total variation explained", col = "grey") +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "PCA dimensions included", y = "Total variation explained") +
  theme_minimal())

ggsave("tv-plot.png", plot = tv_plot, h = 3, w = 6.25)
```

@@

```{r pc-loadings, class.source = 'fold-hide', fig.cap="PC loadings."}
reshape2::melt(as.matrix(E)) %>%
  ggplot(aes(x = Var1, y = Var2, fill = value)) +
  labs(x = "", y = "", fill = "E[i, j]") +
  geom_tile() +
  scale_fill_viridis_c() +
  labs(x = "PC loading", y = "Hyper") +
  theme_minimal()
```

@@

```{r cov-reconstruction, class.source = 'fold-hide', fig.cap="PC loadings."}
E_s <- E[, 1:s]
Lambda_s <- Lambda[1:s, 1:s]
C_s <- E_s %*% Lambda_s %*% t(E_s)

@@

(reduced_rank_plot <- {C_plot + theme(legend.position = "none") + labs(subtitle = "Full rank")} + {C_s_plot + labs(subtitle = "Reduced rank")})

ggsave("reduced-rank-plot.png", reduced_rank_plot, h = 3.5, w = 6.25)
```

Create a function to do the PCA rescaling, which also adapts according to the mean and reweights the nodes:

```{r}
#' @param m Mean vector
#' @param C Covariance matrix
#' @param s Small grid dimension
#' @param k Number of points per small grid dimension
pca_rescale <- function(m, C, s, k) {
  d <- nrow(C)
  stopifnot(d == length(m))
  eigenC <- eigen(C)
  lambda <- eigenC$values
  Lambda <- diag(lambda)
  E <- eigenC$vectors
  E_s <- E[, 1:s] 
  gg_s <- mvQuad::createNIGrid(dim = s, type = "GHe", level = k) 
  nodes_out <- t(E_s %*% diag(lambda[1:s]^{0.5}, ncol = s) %*% t(mvQuad::getNodes(gg_s)))
  for(j in 1:d) nodes_out[, j] <- nodes_out[, j] + m[j]
  weights_out <- mvQuad::getWeights(gg_s) * as.numeric(mvQuad::getWeights(mvQuad::createNIGrid(dim = d - s, type = "GHe", level = 1)))

  # Putting things into a mvQuad format manually
  gg <- mvQuad::createNIGrid(dim = d, type = "GHe", level = 1)
  gg$level <- rep(NA, times = d)
  gg$ndConstruction <- "PCA"
  gg$nodes <- nodes_out
  gg$weights <- weights_out
  return(gg)
}
```

## Testing with simple examples

Here we run some unit tests to make sure, visually and numerically, that the methods are working as expected.

### Gaussian 2D function

A simple 2D Gaussian example:

$$
\begin{pmatrix}
x_1 \\
x_2
\end{pmatrix}
\sim
\mathcal{N}
\left(
\begin{pmatrix}
1 \\
3/2
\end{pmatrix},
\begin{pmatrix}
2 & 1 \\
1 & 1
\end{pmatrix}
\right)
$$

```{r gaussian-2d, class.source = 'fold-hide', fig.cap="Gaussian 2D objective function."}
m <- c(1, 1.5)
C <- matrix(c(2, 1, 1, 1), ncol = 2)

obj <- function(theta) {
  mvtnorm::dmvnorm(theta, mean = m, sigma = C, log = TRUE)
}

ff <- list(
  fn = obj,
  gr = function(theta) numDeriv::grad(obj, theta),
  he = function(theta) numDeriv::hessian(obj, theta)
)

grid <- expand.grid(
  theta1 = seq(-2, 5, length.out = 700),
  theta2 = seq(-2, 5, length.out = 700)
)

ground_truth <- cbind(grid, pdf = exp(obj(grid)))

plot <- ggplot(ground_truth, aes(x = theta1, y = theta2, z = pdf)) +
  geom_contour(col = multi.utils::cbpalette()[1]) +
  coord_fixed(xlim = c(-2, 4.5), ylim = c(-2, 4.5), ratio = 1) +
  labs(x = "", y = "") +
  theme_minimal()

plot
```

Define four AGHQ-PCA grids, with `k` running from 1 to 7:

```{r}
pca_grid_1 <- pca_rescale(m = m, C = C, s = 1, k = 1)
pca_grid_3 <- pca_rescale(m = m, C = C, s = 1, k = 3)
pca_grid_5 <- pca_rescale(m = m, C = C, s = 1, k = 5)
pca_grid_7 <- pca_rescale(m = m, C = C, s = 1, k = 7)
```

For example, the version with 3 points looks as follows:

```{r pca-grid-3, class.source = 'fold-hide', fig.cap="AGHQ-PCA grid for Gaussian with $k = 3$."}
plot_points <- function(gg) {
  plot +
    geom_point(
      data = mvQuad::getNodes(gg) %>%
        as.data.frame() %>%
        mutate(weights = mvQuad::getWeights(gg)),
      aes(x = V1, y = V2, size = weights),
      alpha = 0.8,
      col = multi.utils::cbpalette()[2],
      inherit.aes = FALSE
    ) +
    scale_size_continuous(range = c(1, 2)) +
    labs(x = "", y = "", size = "Weight") +
    theme_minimal()
}

plot_points(pca_grid_3)
```

We can optimise the objective function using the BFGS algorithm to recover the mode and Hessian at the mode.
Of course, for this example, these are known in advance as we are dealing with a Gaussian, but in general this is how they will be computed.

```{r}
opt_bfgs <- aghq::optimize_theta(ff, m, control = default_control(method = "BFGS"))
opt_bfgs$mode
opt_bfgs$hessian
Matrix::forceSymmetric(solve(opt_bfgs$hessian))
```

Now we can perform regular AGHQ with a product grid (again with a range of values for `k`):

```{r}
norm_bfgs_1 <- aghq::normalize_logpost(opt_bfgs, k = 1)
norm_bfgs_3 <- aghq::normalize_logpost(opt_bfgs, k = 3)
norm_bfgs_5 <- aghq::normalize_logpost(opt_bfgs, k = 5)
norm_bfgs_7 <- aghq::normalize_logpost(opt_bfgs, k = 7)
norm_bfgs <- list(norm_bfgs_1, norm_bfgs_3, norm_bfgs_5, norm_bfgs_7)
```

As well as the the AGHQ-PCA grids:

```{r}
norm_pca_bfgs_1 <- local_normalize_logpost(opt_bfgs, basegrid = pca_grid_1, adapt = FALSE)
norm_pca_bfgs_3 <- local_normalize_logpost(opt_bfgs, basegrid = pca_grid_3, adapt = FALSE)
norm_pca_bfgs_5 <- local_normalize_logpost(opt_bfgs, basegrid = pca_grid_5, adapt = FALSE)
norm_pca_bfgs_7 <- local_normalize_logpost(opt_bfgs, basegrid = pca_grid_7, adapt = FALSE)
norm_pca_bfgs <- list(norm_pca_bfgs_1, norm_pca_bfgs_3, norm_pca_bfgs_5, norm_pca_bfgs_7)
```

And a second way of producing the AGHQ-PCA grids directly using `mvQuad`:

```{r, fig.cap="Alternative approach AGHQ-PCA grid for Gaussian with $k = 3$."}
pca2_grid_1 <- mvQuad::createNIGrid(dim = 2, type = "GHe", level = c(1, 1))
mvQuad::rescale(pca2_grid_1, m = m, C = C, dec.type = 1)

pca2_grid_3 <- mvQuad::createNIGrid(dim = 2, type = "GHe", level = c(3, 1))
mvQuad::rescale(pca2_grid_3, m = m, C = C, dec.type = 1)

pca2_grid_5 <- mvQuad::createNIGrid(dim = 2, type = "GHe", level = c(5, 1))
mvQuad::rescale(pca2_grid_5, m = m, C = C, dec.type = 1)

pca2_grid_7 <- mvQuad::createNIGrid(dim = 2, type = "GHe", level = c(7, 1))
mvQuad::rescale(pca2_grid_7, m = m, C = C, dec.type = 1)

plot_points(pca2_grid_3)

norm_pca2_bfgs_1 <- local_normalize_logpost(opt_bfgs, basegrid = pca2_grid_1, adapt = FALSE)
norm_pca2_bfgs_3 <- local_normalize_logpost(opt_bfgs, basegrid = pca2_grid_3, adapt = FALSE)
norm_pca2_bfgs_5 <- local_normalize_logpost(opt_bfgs, basegrid = pca2_grid_5, adapt = FALSE)
norm_pca2_bfgs_7 <- local_normalize_logpost(opt_bfgs, basegrid = pca2_grid_7, adapt = FALSE)
norm_pca2_bfgs <- list(norm_pca2_bfgs_1, norm_pca2_bfgs_3, norm_pca2_bfgs_5, norm_pca2_bfgs_7)
```

The density is already normalised, so it has a normalising constant of 1, and a log normalising constant of $\log(1) = 0$:

```{r, class.source = 'fold-hide', fig.cap="Unit test for the Gaussian example"}
truelognormconst <- 0

results <- data.frame(
  "method" = c("Truth", paste0("aghq, k = ", c(1, 3, 5, 7)), paste0("aghq-pca, k = ", c(1, 3, 5, 7)), paste0("aghq-pca2, k = ", c(1, 3, 5, 7))),
  "lognormconst" = c(truelognormconst, sapply(c(norm_bfgs, norm_pca_bfgs, norm_pca2_bfgs), function(x) x$lognormconst)),
  "type" = c("Truth", rep("AGHQ", 4), rep("AGHQ-PCA", 4), rep("AGHQ-PCA2", 4))
)

ggplot(results, aes(x = method, y = lognormconst, col = as.factor(type))) +
  geom_point(size = 1) +
  labs(x = "Method", y = "Log normalising constant", col = "") +
  scale_color_manual(values = multi.utils::cbpalette()) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 70, vjust = 0.5, hjust = 0.5))
```

### Non-Gaussian 2D function

A more complicated two dimensional function from Alex's [unit tests](https://github.com/awstringer1/aghq/blob/master/tests/testthat/setup-01-optimization.R) for the `aghq` package.

```{r non-gaussian, class.source = 'fold-hide', fig.cap="Non-Gaussian 2D objective function."}
set.seed(84343124)

logfteta <- function(eta, y) {
  n <- length(y)
  n1 <- ceiling(n / 2)
  n2 <- floor(n / 2)
  y1 <- y[1:n1]
  y2 <- y[(n1 + 1):(n1 + n2)]
  eta1 <- eta[1]
  eta2 <- eta[2]
  sum(y1) * eta1 - (length(y1) + 1) * exp(eta1) - sum(lgamma(y1+1)) + eta1 +
    sum(y2) * eta2 - (length(y2) + 1) * exp(eta2) - sum(lgamma(y2+1)) + eta2
}

n1 <- 5
n2 <- 5
n <- n1 + n2
y1 <- rpois(n1, 5)
y2 <- rpois(n2, 5)

truemode <- c(log((sum(y1) + 1) / (length(y1) + 1)), log((sum(y2) + 1) / (length(y2) + 1)))
truelogint <- function(y) lgamma(1 + sum(y)) - (1 + sum(y)) * log(length(y) + 1) - sum(lgamma(y + 1))
truelognormconst <- truelogint(y1) + truelogint(y2)

obj <- function(x) logfteta(x, c(y1, y2))

ff <- list(
  fn = obj,
  gr = function(x) numDeriv::grad(obj, x),
  he = function(x) numDeriv::hessian(obj, x)
)

grid <- expand.grid(
  theta1 = seq(0, 4, length.out = 400),
  theta2 = seq(0, 4, length.out = 400)
)

ground_truth <- data.frame(grid) %>%
  rowwise() %>%
  mutate(pdf = exp(obj(x = c(theta1, theta2))))

plot <- ggplot(ground_truth, aes(x = theta1, y = theta2, z = pdf)) +
  geom_contour(col = multi.utils::cbpalette()[1]) +
  coord_fixed(xlim = c(0.8, 2), ylim = c(0.8, 2), ratio = 1) +
  labs(x = "", y = "") +
  theme_minimal()

plot
```

Optimise using BFSG:

```{r}
opt_bfgs <- aghq::optimize_theta(ff, c(1.5, 1.5), control = default_control(method = "BFGS"))
(m <- opt_bfgs$mode)
(C <- Matrix::forceSymmetric(solve(opt_bfgs$hessian)))
eigen(C)
```

```{r, fig.cap="AGHQ grid for non-Gaussian with $k = 3$."}
grid_bfgs_1 <- mvQuad::createNIGrid(dim = 2, type = "GHe", level = 1)
mvQuad::rescale(grid_bfgs_1, m = m, C = C)

grid_bfgs_3 <- mvQuad::createNIGrid(dim = 2, type = "GHe", level = 3)
mvQuad::rescale(grid_bfgs_3, m = m, C = C)

grid_bfgs_5 <- mvQuad::createNIGrid(dim = 2, type = "GHe", level = 5)
mvQuad::rescale(grid_bfgs_5, m = m, C = C)

grid_bfgs_7 <- mvQuad::createNIGrid(dim = 2, type = "GHe", level = 7)
mvQuad::rescale(grid_bfgs_7, m = m, C = C)

norm_bfgs_1 <- aghq::normalize_logpost(opt_bfgs, 1, 1)
norm_bfgs_3 <- aghq::normalize_logpost(opt_bfgs, 3, 1)
norm_bfgs_5 <- aghq::normalize_logpost(opt_bfgs, 5, 1)
norm_bfgs_7 <- aghq::normalize_logpost(opt_bfgs, 7, 1)
norm_bfgs <- list(norm_bfgs_1, norm_bfgs_3, norm_bfgs_5, norm_bfgs_7)

plot_points(grid_bfgs_3)
```

```{r, fig.cap="AGHQ-PCA grid for non-Gaussian with $k = 3$."}
pca_grid_bfgs_1 <- pca_rescale(m = m, C = C, s = 1, k = 1)
pca_grid_bfgs_3 <- pca_rescale(m = m, C = C, s = 1, k = 3)
pca_grid_bfgs_5 <- pca_rescale(m = m, C = C, s = 1, k = 5)
pca_grid_bfgs_7 <- pca_rescale(m = m, C = C, s = 1, k = 7)

norm_pca_bfgs_1 <- local_normalize_logpost(opt_bfgs, basegrid = pca_grid_bfgs_1, adapt = FALSE)
norm_pca_bfgs_3 <- local_normalize_logpost(opt_bfgs, basegrid = pca_grid_bfgs_3, adapt = FALSE)
norm_pca_bfgs_5 <- local_normalize_logpost(opt_bfgs, basegrid = pca_grid_bfgs_5, adapt = FALSE)
norm_pca_bfgs_7 <- local_normalize_logpost(opt_bfgs, basegrid = pca_grid_bfgs_7, adapt = FALSE)
norm_pca_bfgs <- list(norm_pca_bfgs_1, norm_pca_bfgs_3, norm_pca_bfgs_5, norm_pca_bfgs_7)

plot_points(pca_grid_bfgs_3)
```

```{r, fig.cap="Alternative approach AGHQ-PCA grid for non-Gaussian with $k = 3$."}
pca2_grid_1 <- mvQuad::createNIGrid(dim = 2, type = "GHe", level = c(1, 1))
mvQuad::rescale(pca2_grid_1, m = m, C = C, dec.type = 1)

pca2_grid_3 <- mvQuad::createNIGrid(dim = 2, type = "GHe", level = c(3, 1))
mvQuad::rescale(pca2_grid_3, m = m, C = C, dec.type = 1)

pca2_grid_5 <- mvQuad::createNIGrid(dim = 2, type = "GHe", level = c(5, 1))
mvQuad::rescale(pca2_grid_5, m = m, C = C, dec.type = 1)

pca2_grid_7 <- mvQuad::createNIGrid(dim = 2, type = "GHe", level = c(7, 1))
mvQuad::rescale(pca2_grid_7, m = m, C = C, dec.type = 1)

norm_pca2_bfgs_1 <- local_normalize_logpost(opt_bfgs, basegrid = pca2_grid_1, adapt = FALSE)
norm_pca2_bfgs_3 <- local_normalize_logpost(opt_bfgs, basegrid = pca2_grid_3, adapt = FALSE)
norm_pca2_bfgs_5 <- local_normalize_logpost(opt_bfgs, basegrid = pca2_grid_5, adapt = FALSE)
norm_pca2_bfgs_7 <- local_normalize_logpost(opt_bfgs, basegrid = pca2_grid_7, adapt = FALSE)
norm_pca2_bfgs <- list(norm_pca2_bfgs_1, norm_pca2_bfgs_3, norm_pca2_bfgs_5, norm_pca2_bfgs_7)

plot_points(pca2_grid_3)
```

```{r, class.source = 'fold-hide', fig.cap="Unit test for the non-Gaussian example"}
results <- data.frame(
  "method" = c("Truth", paste0("aghq, k = ", c(1, 3, 5, 7)), paste0("aghq-pca, k = ", c(1, 3, 5, 7)), paste0("aghq-pca2, k = ", c(1, 3, 5, 7))),
  "lognormconst" = c(truelognormconst, sapply(c(norm_bfgs, norm_pca_bfgs, norm_pca2_bfgs), function(x) x$lognormconst)),
  "type" = as.factor(c("Truth", rep("AGHQ", 4), rep("AGHQ-PCA", 4), rep("AGHQ-PCA2", 4)))
)

ggplot(results, aes(x = method, y = lognormconst, col = type)) +
  geom_point(size = 1) +
  labs(x = "Method", y = "Log normalising constant", col = "") +
  scale_color_manual(values = multi.utils::cbpalette()) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 70, vjust = 0.5, hjust = 0.5))
```

@@

gg3 <- pca_rescale(m = m, C = C, s = 3, k = 2)
nrow(mvQuad::getNodes(gg3))

gg5 <- pca_rescale(m = m, C = C, s = 5, k = 2)
nrow(mvQuad::getNodes(gg5))

gg7 <- pca_rescale(m = m, C = C, s = 7, k = 2)
nrow(mvQuad::getNodes(gg7))

gg9 <- pca_rescale(m = m, C = C, s = 9, k = 2)
nrow(mvQuad::getNodes(gg9))
```

>>>>

```{r}
hypers <- names(fit$par)
```

There are `r length(hypers)` hyperparameters, comprised ofa `r data.frame(hypers) %>% filter(str_detect(hypers, "^logit_")) %>% nrow()` on the logit scale, and `r data.frame(hypers) %>% filter(str_detect(hypers, "^log_")) %>% nrow()` on the log scale.

@@

data.frame(par = names(sd), sd = unname(sd)) %>%
  mutate(
    start = str_extract(par, "^[^_]+"),
    scale = fct_recode(start, "Log" = "log", "Logit" = "logit", "Other" = "OmegaT")
  ) %>%
  ggplot(aes(x = reorder(par, sd), y = sd, col = scale)) +
    geom_point(size = 2) +
    coord_flip() +
    scale_color_manual(values = c("#56B4E9","#009E73", "#E69F00")) +
    lims(y = c(0, 2)) +
    theme_minimal() +
    labs(x = "", y = "Marginal standard deviation", col = "Scale")

ggsave("marginal-sd.png", height = 3.5, w = 6.25)
```

@@

The total number of points for this grid is `r prod(base_grid$level)`.
Let's try fitting this, and see how long it takes.
First prepare the data:

@@

```{r}
quad$modesandhessians[, 1:24] %>%
  pivot_longer(cols = everything()) %>%
  mutate(id = rep(1:24, times = 2)) %>%
  ggplot(aes(x = reorder(name, id), y = value)) +
    geom_point(alpha = 0.8) +
    coord_flip() +
    labs(x = "", y = "Value") + 
    theme_minimal()
```

Interesting to note that for the Cholesky adapted grid with `levels = c(1, 1, ..., 2, 1, ..., 1)` there is variation in all of the dimensions greater than or equal to the 16th.
This is related to the Cholesky adaption being based on a lower triangular matrix.
To verify this, we can look at the differences between the two grid points.
For many of the dimensions the difference is too small to see on the plot above.

```{r}
t(unname(diff(as.matrix(quad$modesandhessians[, 1:24]))))
```

@@

```{r}
base_grid_copy <- rlang::duplicate(base_grid)

@@

```{r}
mvQuad::rescale(base_grid_copy, m = quad$optresults$mode, C = Matrix::forceSymmetric(solve(quad$optresults$hessian)), dec.type = 1)
t(diff(mvQuad::getNodes(base_grid_copy)))
```

@@

@@

ggplot(tv_df, aes(x = n, y = tv)) +
  geom_point() +
  geom_hline(yintercept = 0.9, col = "grey", linetype = "dashed") +
  annotate("text", x = 20, y = 0.875, label = "90% of total variation explained", col = "grey") +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "PCA dimensions included", y = "Total variation explained") +
  theme_minimal()

ggsave("total-variation.png", h = 3, w = 6.25)
```

@@

```{r pc-loadings, class.source = 'fold-hide', fig.cap="PC loadings."}
rownames(E) <- hypers

reshape2::melt(as.matrix(E)) %>%
  ggplot(aes(x = Var1, y = factor(Var2), fill = value)) +
  labs(x = "", y = "", fill = "") +
  geom_tile() +
  coord_flip() +
  scale_fill_gradientn(
    colours = c("#E69F00", "white", "#009E73"),
    rescaler = ~ scales::rescale_mid(.x, mid = 0),
    limits = c(-1.1, 1.1)
  ) +
  labs(x = "Hyper", y = "Principal component loading") +
  theme_minimal() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

ggsave("pc-loadings.png", h = 3.5, w = 6.25)
```

@@

```{r cov-reconstruction, class.source = 'fold-hide', fig.cap="Hessian matrix recons."}
E_s <- E[, 1:s]
Lambda_s <- Lambda[1:s, 1:s]
C_s <- E_s %*% Lambda_s %*% t(E_s)

@@

{C_plot + theme(legend.position = "none") + labs(subtitle = "Full rank")} + {C_s_plot + labs(subtitle = "Reduced rank")}

ggsave("reduced-rank.png", h = 3.5, w = 6.25)
```

@@

gg3 <- pca_rescale(m = m, C = C, s = 3, k = 3)
nrow(mvQuad::getNodes(gg3))

gg5 <- pca_rescale(m = m, C = C, s = 5, k = 3)
nrow(mvQuad::getNodes(gg5))

gg7 <- pca_rescale(m = m, C = C, s = 7, k = 3)
nrow(mvQuad::getNodes(gg7))

gg9 <- pca_rescale(m = m, C = C, s = 9, k = 3)
nrow(mvQuad::getNodes(gg9))
```

# Dealing with the scales issue

Put `logit` and `log` on parity somehow!

```{r}
#' TODO!
```
